Succinct representations for abstract interpretation

### 2011-11-01 papers/PLDI2012/implicitization.tex
deplacement paragraphe calcul de P_R

\subsection{Analysis algorithm}
\label{sec:analysis-algorithm}
LLVM bitcode is in \emph{static single assignment} (SSA) form: a given scalar variable is given a value at a single syntactic point in the program. In concrete terms, an assignment \lstinline|x=2*x+1;| gets translated into a definition $x_2 = 2x_1+1$, with distinct variables $x_1$ and $x_2$ corresponding to the same original variable \lstinline|x| at different points in the program.
LLVM makes it easy to follow definition-use and use-definition chains: for a given variable (say, $x_2$) one can immediately obtain its definition (say, $2x_1+1$).
One may see conversion to SSA form as a static precomputation of some of the symbolic propagations proposed by \citet{DBLP:conf/vmcai/Mine06} to enhance the precision of analyses.

@@

We compared the precision of the different techniques described in this article as follows:
\begin{itemize}
\item For each program, we distinguished a set $P_R = P_W$ of suitable widening points by a simple algorithm: for each procedure, we compute the strongly connected components of its control-flow graph using Tarjan's algorithm; the targets of the back-edges of the depth-first search are added to~$P_R$. Note that the resulting set is not necessarily minimal, but is sufficient to disconnect all cycles
(More sophisticated techniques are discussed in e.g. \citet{BourdonclePhd}).
\MM{Pourquoi cet item se trouve dans la section ``Precision of the
  various techniques'' et pas dans la section précédente sur
  l'implem ?}

\item For each program and each pair $(T_1,T_2)$ of analysis techniques, we list
	the proportion of control points in $P_R$ where $T_1$ (resp.~$T_2$) gives a
	strictly stronger invariant, denoted by $\subsetneq$ (resp. $\supsetneq$),
	and the proportion of control points where the invariants given by $T_1$ and
	$T_2$ are uncomparable for the inclusion ordering (the remainder of the
	control points are thus those for which both techniques give the same
	invariant). We use convex polyhedra as the abstract domain.
\end{itemize}

>>>>

\subsection{Analysis algorithm}
\label{sec:analysis-algorithm}
For each program, we distinguish a set $P_R = P_W$ of suitable widening points by a simple algorithm: for each procedure, compute the strongly connected components of its control-flow graph using Tarjan's algorithm; the targets of the back-edges of the depth-first search are added to~$P_R$. Note that the resulting set is not necessarily minimal, but is sufficient to disconnect all cycles --- more sophisticated techniques are discussed in e.g. \citet{BourdonclePhd}.

LLVM bitcode is in \emph{static single assignment} (SSA) form: a given scalar variable is given a value at a single syntactic point in the program. In concrete terms, an assignment \lstinline|x=2*x+1;| gets translated into a definition $x_2 = 2x_1+1$, with distinct variables $x_1$ and $x_2$ corresponding to the same original variable \lstinline|x| at different points in the program.
LLVM makes it easy to follow definition-use and use-definition chains: for a given variable (say, $x_2$) one can immediately obtain its definition (say, $2x_1+1$).
One may see conversion to SSA form as a static precomputation of some of the symbolic propagations proposed by \citet{DBLP:conf/vmcai/Mine06} to enhance the precision of analyses.

@@

For each program and each pair $(T_1,T_2)$ of analysis techniques, we list
the proportion of control points in $P_R$ where $T_1$ (resp.~$T_2$) gives a
strictly stronger invariant, denoted by $\subsetneq$ (resp. $\supsetneq$),
and the proportion of control points where the invariants given by $T_1$ and
$T_2$ are uncomparable for the inclusion ordering (the remainder of the
control points are thus those for which both techniques give the same
invariant). We use convex polyhedra as the abstract domain.
